%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec}
\usepackage{enumitem}
\usepackage{changepage}
% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=6in, textheight=8.5in, marginparsep=8pt, marginparwidth=1in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\normalsize #1}}
\renewcommand*{\raggedrightmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm,
bookmarks, colorlinks, breaklinks,
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Abram Handler - vita},
	pdfauthor={Abe Handler},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

% DOCUMENT
\begin{document}
{\LARGE Abram Handler}\\[.2cm]
Ph.D. student at University of Massachusetts \\
Email: \href{mailto:abram.handler@gmail.com}{abram.handler@gmail.com}\\
URL: www.abehandler.com \\

\vspace{-.5cm}
%%\hrule
\section*{Areas of interest}
Natural language processing • Data science • Human-computer interaction • Machine learning


\section*{Education}

\years{Present}\textsc{Ph.D.} candidate in Computer Science, University of Massachusetts, Amherst \\\\ SLANG Lab: \url{http://slanglab.cs.umass.edu/} \\ Advisor: Brendan O'Connor \\

\years{2018}\textsc{M.S.} in Computer Science, University of Massachusetts, Amherst, GPA 3.8 \\

\years{2014}\textsc{M.S.} in Computer Science, University of New Orleans, GPA 4.0 \\ Advisor: Vassil Roussev \\

\years{2007}\textsc{B.A.} in Philosophy, Columbia University, GPA 3.9 \\

\vspace{-.5cm}

\section*{Teaching and mentoring}

\years{2019} Classroom instructor for first-year seminar on ``Ethics and Artificial Intelligence" (four sections)  \\
\years{2018 - 2019} Group advisor, UMass Industry Mentorship Program (two semesters) \\
\years{2017} Summer graduate coordinator for the REUMass program for undergraduate researchers \\ 
\years{2016-2018} Teaching assistant for graduate courses in graphical models and natural language processing (three semesters) \\
\years{2016} Mentor to visiting undergraduate researcher, Michael Pinkham 

\section*{Refereed Conference Papers}

Query-focused Sentence Compression in Linear Time. \textbf{Abram Handler} and Brendan O'Connor. \textit{EMNLP, 2019}.\\ \\
Investigating Sports Commentator Bias within a Large Corpus of American Football Broadcasts. Jack Merullo, Luke Yeh, \textbf{Abram Handler}, Alvin Grissom II, Brendan O'Connor and Mohit Iyyer. \textit{EMNLP, 2019}.\\ \\
Relational Summarization for Corpus Analysis. \textbf{Abram Handler} and Brendan O'Connor. \textit{NAACL, 2018}.\\ \\
Identifying civilians killed by police with distantly supervised entity-event extraction. Katherine Keith, \textbf{Abram Handler}, Michael Pinkham, Cara Magliozzi, Joshua McDuffie, and Brendan O'Connor. \textit{EMNLP, 2017}. 

\section*{Refereed Workshop Papers}

Rookie: A unique approach for exploring news archives. \textbf{Abram Handler} and Brendan O'Connor. \textit{Data Science + Journalism workshop at KDD, 2017}. \\ \\ 
Bag of What? Simple Noun Phrase Extraction for Text Analysis. \textbf{Abram Handler}, Matthew J. Denny, Hanna Wallach, and Brendan O'Connor. \textit{Text as Data, 2016} and \textit{NLP + Computational Social Science workshop at EMNLP, 2016}.\\ \\
Visualizing textual models with in-text and word-as-pixel highlighting.  \textbf{Abram Handler}, Su Lin Blodgett and Brendan O'Connor. \textit{Workshop on Human Interpretability in Machine Learning at ICML, 2016} 

\section*{Preprints}
Human acceptability judgements for extractive sentence compression. \textbf{Abram Handler}, Brian Dillon, Brendan O'Connor \textit{https://arxiv.org/abs/1902.00489}, 2019. 

\section*{Grants}
\years{2015} Abram Handler, Steve Myers, Anne Mueller, Knight Prototype Foundation Fund, ``Semantic Timeline Maker." Funded initial development of the \textit{Rookie} text analytics system. \\
\years{2018-2019} Brendan O’Connor, Abram Handler, Brian Dillon.  Figure Eight, Inc.  AI for Everyone Challenge.  “Crowdsourced tree edit supervision for flexible sentence summarization and corpus exploration.”

\section*{Awards}
\years{2018} \textbf{Best reviewer award} at EMNLP conference (top 7\%) \\
\years{2015} \textbf{Excellence in journalism award}, New Orleans press club \\
\years{2014} \textbf{Doctoral scholarship (declined)}, University of New Orleans \\
\years{2007} \textit{\textbf{Magna cum laude}}, Columbia University \\
\years{2007-2003} \textbf{Dean's list}, Columbia University (five semesters) \\
\years{2006} \textbf{Oxbridge scholars program}, Columbia University - Cambridge University  \\
\years{2003} \textbf{John Jay Scholar}, Columbia University 

\section*{Skills \& software projects}

\years{2006-\\present} \textbf{Programming} \\ Longtime, self-taught programmer fluent in Python, NumPy, PyTorch, HTML/CSS, JavaScript, React, Redux, SQL/object relational mappers, Flask, git, Linux and systems administration. \\

\years{2016} \textbf{Phrasemachine} \\
Developed widely-used \texttt{Python} package for finding phrases \\ \url{https://github.com/slanglab/phrasemachine}. \\

\years{2014-2015}\textbf{Live election maps} \\ Leader of technical team which produced the first three live election maps in Louisiana \\ \url{http://elections.thelensnola.org}  \\ \\

\years{2014} \textbf{Document Cloud (Doc Split)} \\ Open source contributor: added support for the Tesseract rotation detection plugin \\
\url{https://www.documentcloud.org}

\section*{Work Experience}

\years{2015-present}\textbf{University of Massachusetts}, Research assistant and teaching assistant, Amherst, MA \\
- Conduct both individual and group research projects as member of SLANG lab. \\

\years{2019}\textbf{BuzzFeed}, Data science intern, New York, NY \\
- Contributed to internal API for analyzing user comments. \\ 
- Developed a new method for detecting entity aliases, using comment data. \\

\years{2018}\textbf{Agolo}, Natural language processing research intern, New York, NY \\
- Implemented state-of-the-art sentence compression technique in PyTorch. \\ 
- Developed a new method for summarizing entity relationships in news corpora. \\

\years{2014-2015}\textbf{The Lens}, Software developer and data journalist, New Orleans, LA \\
- Founded and lead a news applications team. \\
- Produced interactive web stories. \\
- Analyzed heterogeneous textual records to programmatically identify corruption. \\

\years{2013}\textbf{C4 Tech and Design}, Software developer, New Orleans, LA \\
- Worked as full-stack web developer using PHP, Git, Drupal, Javascript, CSS and HTML.  \\

\years{2011-2013}\textbf{Louisiana Office of Public Health} (Acadiana CARES), Software developer, New Orleans, LA \\ 
- Successfully refactored a mission-critical system for collecting and monitoring electronic lab reports.  \\

\years{2010}\textbf{Jefferson Parish Public Schools}, Digital Opportunity Trust Intern, Gretna, LA \\ 
- Helped develop a new personnel system in PHP, SQL, CSS, HTML and JavaScript.  \\

\years{2007-2009}\textbf{The Bronx Defenders}, Investigator, Bronx, NY \\ 
- Assisted attorneys at a  \textit{pro bono} legal clinic. \\

\years{2006}\textbf{Benenson Strategy Group}, Intern, Manhattan, NY \\ 
- Taught myself to program by automating routine tasks in Microsoft Excel.

\section*{Professional Service}
- Reviewer: EMNLP (2017,2018,2019), ACL (2019, 2020), NAACL (2019), WNUT (2019), New Frontiers in Summarization (2019), ICWSM (2018, 2019, 2020)

\section*{Graduate coursework}

Graduate courses (University of Massachusetts): Machine Learning, Natural Language Processing, Deep Learning, Advanced Algorithms, Theory of Computation, Graphical Models, Reinforcement Learning, Programming Languages and Statistical Machine Learning.

\begin{center}
{\scriptsize  Last updated: \today\-
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
\\}
\end{center}

\end{document}
