%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
%
% This is where the packages are declared

\documentclass[]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{dirtytalk}
\theoremstyle{definition}
\newtheorem{exmp}{Example}[section]

\begin{document}


\title{INFO 2301: Quantitative Reasoning for Information Science}
\author{Abe Handler \\ Department of Information Science \\ University of Colorado, Boulder}
\date{\today}

\maketitle

\begin{abstract}
An outline of what we've covered so far. You should be comfortable with everything in this document. 
\end{abstract}

\section{Sets}

A \textbf{set} is an unordered collection of items, without duplicates. 

People follow a number of conventions when talking about sets.

\begin{itemize}
    \item The items in a set are often called ``elements''
    \item We use capital letters to name sets
    \item We show the elements in a set using curly brackets
    \item A set can include any kind of element (e.g.\ strings, or kinds of apple)
\end{itemize}

\begin{exmp}
We can write the integers between 0 and 3 (including 0 and 3) as $A$ = $\{0,1,2,3\}$
\end{exmp}

\begin{exmp}
Because sets do not have order, if $ B= \{0,1\}$ and $C=\{1,0\}$, then $C=B$.
\end{exmp}

\begin{exmp}
A set of strings, $ P= \{ \text{\say{Denver},\say{Boulder},\say{Broomfield}} \}$
\end{exmp}

\begin{itemize}
    \item If $a$ is an element in $X$ then, we use the notation $a \in X$ 
    \item If $a \in X$ then we say that ``$a$ is in $X$''
    \item We write this: \verb|$a \in X$|
    \item If $a \notin X$ then we say that ``$a$ is not in $X$''
    \item We write this: \verb|$a \notin X$|
\end{itemize}

\begin{exmp}
Let $ C= \{1, 2\}$. Then $1 \in C$ and $6 \notin C$
\end{exmp}


\subsection{Subsets}

If all elements of $A$ are elements of $B$ then we say that $A$ is a subset of $B$.  We use the notation $ A \subset B$ (written \verb|$ A  \subset B $|) to indicate that $A$ is a subset of $B$.

\begin{exmp}\label{e:subset}
Let $ A= \{2, 1\}$ and $B = \{1,2,5\}$. Then $A \subset B$
\end{exmp}

In this class, when we use $ A \subset B$ we will assume that some elements of $B$ are not elements of $A$. So $A$ is a ``proper subset'' of $B$. For instance, in Example \ref{e:subset}, $A \subset B$ because $5 \in B$ and $5 \notin A$. If we want to allow for the possibility that $A=B$, we can use the notation $A \subseteq B$ (written \verb|$ A \subseteq B $|). 

\begin{exmp}
Let $ A= \{1, 2,3 \}$ and $B = \{1,2,3\}$. Then $A \subseteq B$ but not $A \subset B$
\end{exmp}

\begin{exmp}
Let $ A= \{1, 3 \}$ and $B = \{1,2,3\}$. Then $A \subseteq B$ and $A \subset B$
\end{exmp}

\subsection{Intersections, unions and complements}

\begin{itemize}

\item We use the notation $A \cap B$ (written \verb|$ A  \cap B $|) to indicate all of the elements that are in \textit{both} $A$ and $B$. This is called the \textit{intersection} of $A$ and $B$

\item We use the notation $A \cup B$ (written \verb|$ A  \cup B $|) to indicate all of the elements that are in $A$ or $B$. This is called the \textit{union} of $A$ and $B$.

\item To understand intersections and unions it is often helpful to draw venn diagrams. 

\end{itemize}

\begin{exmp}
Let $ A= \{1, 2, 3\}$ and $B = \{2,3,7\}$. Then $A \cap B$ = $\{2, 3\}$ and $A \cup B$ = $\{1,2, 3, 7\}$
\end{exmp}

\begin{itemize}
\item The complement of a set $A$ is the set of all elements that are not in $A$
\item The complement of a set requires defining $U$, the universal set of all possible elements
\item We write the complement of $A$ as $\overline{A}$ (written \verb|$ \overline{A} $| 
\item We can also write the complement as $A^c$  (written \verb|$ A^c $|)
\end{itemize}

\begin{exmp}
Let $ U= \{1, 2, 3\}$ and $A = \{2\}$. Then $\overline{A}$ = $\{1, 3\}$ 
\end{exmp}

\subsection{Cardinality}

The number of items in a set is called the \textit{cardinality} of the set. We use the notation $\vert F \vert$ (written \verb|$ \vert F \vert $|) to indicate the cardinality of a set.

\begin{exmp}
Let $ F = \{1, -2, 42 \}$, then $\vert F \vert$ = 3
\end{exmp}

\textit{If you spot any errors in this document, or if anything is needlessly confusing, please send me an email. I will assign extra credit.}

\section{Functions}

\begin{itemize}
\item A function maps elements from one set to another. 
\item The first set is called the domain.
\item The second set is called the range. 
\item A function maps each element from the domain to exactly one element in the range.
\item We write this $f: A \rightarrow B$ where $f$ is a function mapping elements of $A$ to $B$ (written \verb|$f: A \rightarrow B $|) 
\end{itemize}

\begin{exmp}
Let $A$ be a set $\{0,1,2,3\}$ and let $f$ be a function mapping every element of $A$ to -19. The domain of $f$ is $A$ and the range is $\{-19\}$
\end{exmp}

\begin{exmp}
Let $A$ be the set of all integers and let $B$ be the set of all integers. The \texttt{addOne} function maps each element in $A$ to the element in $B$ that is exactly one greater. For instance, the \texttt{addOne} function maps 4 to 5.
\end{exmp}

\section{Vectors}

\begin{itemize}
\item A vector is a list of numbers. 
\item Each number in the vector is called a ``component'' and represents a dimension of the vector. 
\item We denote vectors with bold, lower-case letters and triangle brackets, such as $ \mathbf{x}=<1,2> $ (written \verb|$  \mathbf{x}=<1,2> $|)
\item We can use subscripts to refer to components of a vector. If $\mathbf{x}=<6,9>$ then $\mathbf{x}_1$ = 6 (assuming indexing starting at one)
\end{itemize}

\subsection{Vector addition}

Vector addition is an operation which takes two input vectors and returns one output vector. If  $\mathbf{x}=<x_1, x_2 ... x_n>$ and $\mathbf{y}=<y_1, y_2 ... y_n>$  then  $\mathbf{x}+\mathbf{y}=<x_1 + y_1, x_2 + y_2 ... x_n + y_n>$.

\begin{exmp}
$\mathbf{x}=<3,4>$ and $\mathbf{y}=<-1,2>$  then  $\mathbf{x}+\mathbf{y}=<2,6>$
\end{exmp}

\subsection{Summation notation}

Summation notation is important for vector operations, and in many other areas of math. 

\begin{itemize}
\item To indicate the sum a sequence of items, we write $\Sigma_{i=0}^Nx_i$ where $x_i$ is the $i$th item in a sequence. 
\item You can read this as summing over a sequence of items, from item 0 to item $N$. 
\item You can think of $i$ as an index into the sequence, in the same way you may think of $i$ as an index into an array. 
\item We write this as \verb|$ \Sigma_i=0^Nx_i$|)
\end{itemize}

\begin{exmp}
If we have a sequence $x=(3, 4, 5)$  then $\Sigma_{i=1}^{N=3} x_i = 3 + 4 + 5 = 12$
\end{exmp}

You can also use this notation to describe the sum of items in a sequence, after applying some operation.

\begin{exmp}
$\Sigma_i=1^5x_i^2 = 1^2 + 2^2 + 3^2 + 4^2 + 5^2 = 1 + 4 + 9 + 16 + 25 = 55$
\end{exmp}

\subsection{Euclidean norm}

The Euclidean norm of a vector is  $\vert \vert x \vert \vert_2$ = $\sqrt{\Sigma_{i=1}^{N} x_i ^2}$. You can think of the Euclidean norm as the size of a vector. 
\begin{exmp}
If $ \mathbf{x}=<-2,2> $ then  $\vert \vert x \vert \vert_2$ = $\sqrt{-2^2 + 2^2} = \sqrt{4 + 4}  = \sqrt{8}$  
\end{exmp}

\noindent Note: There are also other norms, which offer other ways of defining the size of a vector.

\end{document}